Austria's Covid legislation: The remarkable absence of authorship in public submissions to the consultative process

### 2021-03-16 _post/2021-03-10-covidsubmissionsnoauthor/covidsubmissionsnoauthor.Rmd
font
revert to original font

```{r setup, include=FALSE, code_collapse=NULL}
library(tidyverse)

@@

```{r, echo=F, code_folding=NULL}
girafe(ggobj = pl_public,
       height_svg = 4.5,
       options = list(
    opts_toolbar(saveaspng = FALSE),
    opts_tooltip(css = glue::glue("background-color:{plot_bg_color}; 
                 line-height:100%;
                 color:black;
                 font-size:80%;
                 font-family:'Roboto Condensed';)"))
  ))
```

>>>>

```{r setup, include=FALSE, code_collapse=NULL}
library(tidyverse)
library(svglite)

library(hrbrthemes)

@@

```{r, echo=F, code_folding=NULL, dev="svglite"}
girafe(ggobj = pl_public,
       height_svg = 4.5,
  #     font=list(sans="Roboto"),
       options = list(
    opts_toolbar(saveaspng = FALSE),
    opts_tooltip(css = glue::glue("background-color:{plot_bg_color}; 
                 line-height:100%;
                 color:black;
                 font-size:80%;
                 font-family:'Roboto Condensed';)"))
  ))
```
